Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
corrected algorithm
conclusion

\Ram{Matt can you please take a crack at this ....}
Avenues of improvement:
update predictions when given additional measurements

The conclusion goes here.

>>>>

\Ram{Matt can you please take a crack at this ....}
This paper presents a real-time approach to probabilistic pedestrian modeling. We demonstrate the ability to accurately predict the final location of a pedestrian with comparable accuracy to a state-of-the-art with large gains in three critical areas: 1) prediction speed is highly efficient enabling tight loop real-time control;  2) our prediction uncertainty bound much more accurately reflect potential paths for the human limiting false negatives and maximize the utility and safety of the predictions; and 3) the prediction made by the proposed approach do not require knowledge of the end point  making them applicable to a much wider variety of real world applications. These three features have great promise for robotic applications and we see the integration of such techniques with autonomous system control as one pathway to enable safer operations in shared human-robot spaces. For future directions we plan to optimize the naive python implementation using GPU parallelization to further increase speed and ease integration into system's control loop.
